Comparison of C inn observations

### 2025-03-19 carbon_paper/tex/main.tex
updated figure

\begin{figure*}
\centering
\includegraphics[]{figures/summary.pdf}
\caption[]{
\dbnote{Should citations be moved outside of caption for reader's sake?}
\dbnote{Remove connecting lines on MW HII regions. Should I plot outliers at all?}.
\dbnote{unfortunantly the models in this figure are not consistent with this draft, accedentily deleted/didn't save some of the observed data and will fix in next draft.}
Gas-phase C abundances. 
We plot the fiducial model's present-day ISM abundances as a thick blue line.
Black lines are single-zone models: a fiducial yields and MW-like model (solid black), and three corrected yield models representing the MW (dotted), GSE (dashed) and Wukong (dash-dots).
Points represent measurements in 
    Milky Way stars \citep[yellow stars;][]{amarsi+19},
    MW HII regions \citep[orange pentagons][]{mendez-delgado+22}
    extragalactic RL HII regions \citep[green open diamonds;][]{peimbert+05, skillman+20, toribio-san-cipriano+16, toribio-san-cipriano+17, esteban+14, esteban+09}
    extragalactic CEL HII regions \citep[green full diamonds;][]{garnett+95, senchyna+17, izotov+thuan99, garnett+99, berg+16, berg+19, pena-guerrero+17}
    high redshift galaxies \citep[pink squares, CEL lines;][]{steidel+16, stark+14, matthee+21, mainali+20, jones+23, amorin+17, iani+23, james+14, erb+10, bayliss+14, berg+18, christensen+12, arellano-cordova+2022},
    and
    damped Lyman-alpha (DLA) systems \citep[rust triangles;][]{omera+01, cooke+14, welsh+22, ellison+10, welsh+20, cooke+18, riemer-sorensen+17, DZ+03, cooke+17, cooke+11, dutta+14, morrison+16, srianand+10, pettini+08, kislitsyn+24, cooke+15}.

>>>>

\begin{figure*}
\centering
\includegraphics[]{figures/summary.pdf}
\caption[]{
\dbnote{Should citations be moved outside of caption for reader's sake?}
\dbnote{Remove connecting lines on MW HII regions. Should I plot outliers at all?}.
Gas-phase C abundances. 
We plot the fiducial model's present-day ISM abundances as a thick blue line.
Black lines are single-zone models: a fiducial yields and MW-like model (solid black), and three corrected yield models representing the MW (dotted), GSE (dashed) and Wukong (dash-dots).
Points represent measurements in 
    Milky Way stars \citep[yellow stars;][]{amarsi+19},
    MW HII regions \citep[orange pentagons][]{mendez-delgado+22, esteban+05, esteban+13}
    extragalactic RL HII regions \citep[green open diamonds;][]{peimbert+05, skillman+20, toribio-san-cipriano+16, toribio-san-cipriano+17, esteban+14, esteban+09}
    extragalactic CEL HII regions \citep[green full diamonds;][]{garnett+95, senchyna+17, izotov+thuan99, garnett+99, berg+16, berg+19, pena-guerrero+17}
    high redshift galaxies \citep[pink squares, CEL lines;][]{steidel+16, stark+14, matthee+21, mainali+20, jones+23, amorin+17, iani+23, james+14, erb+10, bayliss+14, berg+18, christensen+12, arellano-cordova+2022},
    and
    damped Lyman-alpha (DLA) systems \citep[rust triangles;][]{omera+01, cooke+14, welsh+22, ellison+10, welsh+20, cooke+18, riemer-sorensen+17, DZ+03, cooke+17, cooke+11, dutta+14, morrison+16, srianand+10, pettini+08, kislitsyn+24, cooke+15}.

### 2025-03-19 carbon_paper/tex/survey_comparison.tex
updated figure

\begin{table}
\centering
\begin{tabular}{lrlll}
\hline
QSO & redshift & C/O & O/H & study \\
\hline
HS 0105+1619 & 2.535998 & $0.23 \pm 0.07$ & $-1.75 \pm 0.03$ & omera+01 \\
J1358+6522 & 3.067259 & $-0.27 \pm 0.06$ & $-2.34 \pm 0.06$ & cooke+14 \\
J0955+4116 & 3.279908 & $-0.46 \pm 0.15$ & $-2.47 \pm 0.06$ & welsh+2022 \\
J0140-0839 & 3.696000 & $-0.30 \pm 0.08$ & $-2.77 \pm 0.15$ & ellison+10 \\
J0035-0918 & 2.340064 & $-0.12 \pm 0.14$ & $-2.47 \pm 0.06$ & welsh+20 \\
Q1243+307 & 2.525640 & $0.24 \pm 0.03$ & $-2.79 \pm 0.03$ & cooke+18 \\
PKS1937-101 & 3.572400 & $1.56 \pm 0.13$ & $-2.57 \pm 0.13$ & riemer-sorensen+17 \\
Q1101-264 & 1.838000 & $0.77 \pm 0.09$ & $-1.66 \pm 0.07$ & dessauges-zavadsky+03 \\
Q2059-360 & 2.507000 & $-0.41 \pm 0.28$ & $-1.38 \pm 0.23$ & dessauges-zavadsky+03 \\
J2155+1358 & 4.212000 & $-0.29 \pm 0.08$ & $-1.82 \pm 0.11$ & dessauges-zavadsky+03 \\
J0903+2628 & 3.077590 & $-0.38 \pm 0.04$ & $-3.07 \pm 0.05$ & cooke+17 \\
J0311-1722 & 3.734000 & $-0.42 \pm 0.11$ & $-2.31 \pm 0.10$ & cooke+11 \\
J1001+0343 & 3.078000 & $-0.41 \pm 0.03$ & $-2.67 \pm 0.05$ & cooke+11 \\
J0953-0504 & 4.202870 & $-0.50 \pm 0.03$ & $-2.57 \pm 0.10$ & dutta+14 \\
Q1202+3235 & 4.977000 & $0.20 \pm 0.09$ & $-2.00 \pm 0.12$ & morrison+16 \\
J1337+3152 & 3.167000 & $-0.19 \pm 0.11$ & $-2.69 \pm 0.17$ & srianand+10 \\
Q0913+072 & 2.618000 & $-0.39 \pm 0.05$ & $-2.42 \pm 0.04$ & pettini+08 \\
J1016+4040 & 2.816000 & $-0.21 \pm 0.05$ & $-2.48 \pm 0.11$ & pettini+08 \\
J1558+4053 & 2.553000 & $-0.06 \pm 0.07$ & $-2.47 \pm 0.06$ & pettini+08 \\
Q2206-199 & 2.076000 & $-0.38 \pm 0.04$ & $-2.09 \pm 0.05$ & pettini+08 \\
J1332+0052 & 3.421086 & $-0.03 \pm 0.02$ & $-1.72 \pm 0.02$ & kislitsyn+24 \\
J1111+1332 & 2.270000 & $-0.18 \pm 0.11$ & $-1.94 \pm 0.08$ & cooke+15 \\
\hline
\end{tabular}
\end{table}
C abundances are measured in XXXX.

Hello

@@

Mrk 1087 & NaN & $0.40 \pm 0.33$ & $-0.40 \pm 0.14$ & pena-guerreno+17 \\
NGC 1741 & NaN & $-0.21 \pm 0.30$ & $-0.56 \pm 0.10$ & pena-guerreno+17 \\
Mrk 5 & NaN & $-0.80 \pm 0.29$ & $-0.83 \pm 0.10$ & pena-guerreno+17 \\

@@

Arp 252 & NaN & $0.06 \pm 0.34$ & $-0.68 \pm 0.15$ & pena-guerreno+17 \\

@@

POX 4 & NaN & $-0.49 \pm 0.14$ & $-0.75 \pm 0.05$ & pena-guerreno+17 \\

@@

SBS 1415+437 & NaN & $-1.42 \pm 0.24$ & $-1.25 \pm 0.07$ & pena-guerreno+17 \\

@@

III Zw 107 & NaN & $-0.51 \pm 0.28$ & $-0.59 \pm 0.10$ & pena-guerreno+17 \\

@@

\begin{longtable}{lllll}
\hline
galaxy & region & C/O & O/H & study \\
\hline
NGC 6822 & region V & $-0.15 \pm 0.21$ & $-0.44 \pm 0.09$ & peimbert+05 \\
MW & Sh 2-311 & $-0.10 \pm 0.14$ & $-0.24 \pm 0.05$ & mendez-delgado+22 \\
MW & NGC 2579 & $-0.14 \pm 0.09$ & $-0.26 \pm 0.03$ & mendez-delgado+22 \\
MW & NGC 3576 & $-0.02 \pm 0.08$ & $-0.08 \pm 0.04$ & mendez-delgado+22 \\
MW & NGC 3603 & $0.04 \pm 0.12$ & $-0.10 \pm 0.05$ & mendez-delgado+22 \\
MW & M8 & $0.04 \pm 0.10$ & $-0.11 \pm 0.04$ & mendez-delgado+22 \\
MW & M16 & $0.03 \pm 0.15$ & $-0.01 \pm 0.05$ & mendez-delgado+22 \\
MW & M17 & $0.26 \pm 0.06$ & $-0.06 \pm 0.02$ & mendez-delgado+22 \\
MW & M20 & $0.02 \pm 0.25$ & $-0.10 \pm 0.06$ & mendez-delgado+22 \\
MW & M42 & $0.03 \pm 0.07$ & $-0.16 \pm 0.02$ & mendez-delgado+22 \\
M101 & H1013 & $0.17 \pm 0.07$ & $-0.24 \pm 0.02$ & skillman+20 \\
M101 & H1052 & $0.13 \pm 0.04$ & $-0.24 \pm 0.01$ & skillman+20 \\
M101 & NGC 5461 & $-0.10 \pm 0.12$ & $-0.33 \pm 0.02$ & skillman+20 \\
M101 & NGC 5462 & $-0.18 \pm 0.19$ & $-0.36 \pm 0.05$ & skillman+20 \\
M101 & NGC 5462 & $-0.07 \pm 0.12$ & $-0.38 \pm 0.01$ & skillman+20 \\
M101 & NGC 5455 & $-0.13 \pm 0.11$ & $-0.42 \pm 0.02$ & skillman+20 \\
M101 & NGC 5447 & $-0.09 \pm 0.09$ & $-0.39 \pm 0.01$ & skillman+20 \\
M101 & NGC 5447 & $-0.04 \pm 0.17$ & $-0.46 \pm 0.01$ & skillman+20 \\
M101 & H1216 & $-0.42 \pm 0.50$ & $-0.55 \pm 0.03$ & skillman+20 \\
M101 & NGC 5471 & $-0.26 \pm 0.46$ & $-0.67 \pm 0.03$ & skillman+20 \\
NGC 300 & R20 & $-0.01 \pm 0.22$ & $-0.12 \pm 0.11$ & toribo-san-cipriano+16 \\
NGC 300 & R23 & $-0.22 \pm 0.23$ & $-0.11 \pm 0.13$ & toribo-san-cipriano+16 \\
NGC 300 & R14 & $-0.15 \pm 0.21$ & $-0.19 \pm 0.11$ & toribo-san-cipriano+16 \\
NGC 300 & R2 & $-0.31 \pm 0.22$ & $-0.24 \pm 0.12$ & toribo-san-cipriano+16 \\
M33 & NGC 588 & $-0.26 \pm 0.19$ & $-0.32 \pm 0.09$ & toribo-san-cipriano+16 \\
M33 & IC 132 & $-0.12 \pm 0.15$ & $-0.34 \pm 0.12$ & toribo-san-cipriano+16 \\
LMC & 30 Dor & $-0.29 \pm 0.06$ & $-0.28 \pm 0.04$ & toribo-san-cipriano+17 \\
LMC & N44C & $-0.22 \pm 0.03$ & $-0.23 \pm 0.02$ & toribo-san-cipriano+17 \\
LMC & IC 2111 & $-0.21 \pm 0.08$ & $-0.20 \pm 0.07$ & toribo-san-cipriano+17 \\
LMC & NGC 1714 & $-0.24 \pm 0.07$ & $-0.25 \pm 0.07$ & toribo-san-cipriano+17 \\
LMC & N11B & $-0.27 \pm 0.04$ & $-0.22 \pm 0.02$ & toribo-san-cipriano+17 \\
SMC & N66A & $-0.46 \pm 0.06$ & $-0.46 \pm 0.03$ & toribo-san-cipriano+17 \\
SMC & N81 & $-0.46 \pm 0.04$ & $-0.47 \pm 0.02$ & toribo-san-cipriano+17 \\
SMC & NGC 456 & $-0.41 \pm 0.19$ & $-0.45 \pm 0.09$ & toribo-san-cipriano+17 \\
SMC & N88A & $-0.33 \pm 0.03$ & $-0.59 \pm 0.02$ & toribo-san-cipriano+17 \\
NGC 6822 & centre & $-0.31 \pm 0.15$ & $-0.46 \pm 0.05$ & esteban+14 \\
NGC 5408 & centre & $-0.41 \pm 0.19$ & $-0.60 \pm 0.04$ & esteban+14 \\
M31 & K932 & $0.05 \pm 0.16$ & $-0.19 \pm 0.03$ & esteban+09 \\
M33 & NGC 595 & $0.05 \pm 0.17$ & $-0.12 \pm 0.05$ & esteban+09 \\
M33 & NGC 604 & $0.01 \pm 0.14$ & $-0.21 \pm 0.03$ & esteban+09 \\
NGC 2366 & NGC-2363 & $-0.08 \pm 0.14$ & $-0.77 \pm 0.05$ & esteban+09 \\
NGC 2403 & VS 24 & $0.30 \pm 0.28$ & $-0.44 \pm 0.04$ & esteban+09 \\
NGC 2403 & VS 38 & $0.42 \pm 0.20$ & $-0.52 \pm 0.05$ & esteban+09 \\
NGC 2403 & VS 44 & $-0.08 \pm 0.22$ & $-0.20 \pm 0.04$ & esteban+09 \\
\hline
\end{longtable}

>>>>

\begin{table}
    \caption{Damped lynam alpha abundance}
    \centering
    \begin{tabular}{lrlll}
    \hline
    QSO & redshift & C/O & O/H & study \\
    \hline
    HS 0105+1619 & 2.535998 & $0.18 \pm 0.07$ & $-1.86 \pm 0.03$ & omera+01 \\
    J1358+6522 & 3.067259 & $-0.32 \pm 0.06$ & $-2.44 \pm 0.06$ & cooke+14 \\
    J0955+4116 & 3.279908 & $-0.51 \pm 0.15$ & $-2.57 \pm 0.06$ & welsh+2022 \\
    J0140-0839 & 3.696000 & $-0.35 \pm 0.08$ & $-2.87 \pm 0.15$ & ellison+10 \\
    J0035-0918 & 2.340064 & $-0.17 \pm 0.14$ & $-2.57 \pm 0.06$ & welsh+20 \\
    Q1243+307 & 2.525640 & $0.19 \pm 0.03$ & $-2.89 \pm 0.03$ & cooke+18 \\
    PKS1937-101 & 3.572400 & $1.51 \pm 0.13$ & $-2.68 \pm 0.13$ & riemer-sorensen+17 \\
    Q1101-264 & 1.838000 & $0.72 \pm 0.09$ & $-1.76 \pm 0.07$ & dessauges-zavadsky+03 \\
    Q2059-360 & 2.507000 & $-0.46 \pm 0.28$ & $-1.48 \pm 0.23$ & dessauges-zavadsky+03 \\
    J2155+1358 & 4.212000 & $-0.34 \pm 0.08$ & $-1.92 \pm 0.11$ & dessauges-zavadsky+03 \\
    J0903+2628 & 3.077590 & $-0.43 \pm 0.04$ & $-3.17 \pm 0.05$ & cooke+17 \\
    J0311-1722 & 3.734000 & $-0.47 \pm 0.11$ & $-2.41 \pm 0.10$ & cooke+11 \\
    J1001+0343 & 3.078000 & $-0.46 \pm 0.03$ & $-2.77 \pm 0.05$ & cooke+11 \\
    J0953-0504 & 4.202870 & $-0.55 \pm 0.03$ & $-2.67 \pm 0.10$ & dutta+14 \\
    Q1202+3235 & 4.977000 & $0.15 \pm 0.09$ & $-2.10 \pm 0.12$ & morrison+16 \\
    J1337+3152 & 3.167000 & $-0.24 \pm 0.11$ & $-2.79 \pm 0.17$ & srianand+10 \\
    Q0913+072 & 2.618000 & $-0.44 \pm 0.05$ & $-2.52 \pm 0.04$ & pettini+08 \\
    J1016+4040 & 2.816000 & $-0.26 \pm 0.05$ & $-2.58 \pm 0.11$ & pettini+08 \\
    J1558+4053 & 2.553000 & $-0.11 \pm 0.07$ & $-2.57 \pm 0.06$ & pettini+08 \\
    Q2206-199 & 2.076000 & $-0.43 \pm 0.04$ & $-2.19 \pm 0.05$ & pettini+08 \\
    J1332+0052 & 3.421086 & $-0.08 \pm 0.02$ & $-1.83 \pm 0.02$ & kislitsyn+24 \\
    J1111+1332 & 2.270000 & $-0.23 \pm 0.11$ & $-2.04 \pm 0.08$ & cooke+15 \\
    \hline
    \end{tabular}
\end{table}

\begin{table}
    \caption{CEL-derived C abundances from the literature.}

@@

    Mrk 1087 & NaN & $0.40 \pm 0.35$ & $-0.40 \pm 0.16$ & pena-guerreno+17 \\
    NGC 1087 & NaN & $-0.21 \pm 0.30$ & $-0.56 \pm 0.10$ & pena-guerreno+17 \\
    Mrk 5 & NaN & $-0.78 \pm 0.29$ & $-0.85 \pm 0.10$ & pena-guerreno+17 \\

@@

    ARP 252 & NaN & $0.06 \pm 0.34$ & $-0.68 \pm 0.15$ & pena-guerreno+17 \\

@@

    POX 4 & NaN & $-0.48 \pm 0.13$ & $-0.76 \pm 0.05$ & pena-guerreno+17 \\

@@

    SBS 1415+437 & NaN & $-1.43 \pm 0.30$ & $-1.25 \pm 0.09$ & pena-guerreno+17 \\

@@

    III Zw 107 & NaN & $-0.96 \pm 0.28$ & $-0.59 \pm 0.10$ & pena-guerreno+17 \\

@@

\end{table}

\begin{table}
    \caption{RL derived abundances for MW and nearby galaxies
        note that mendez--delgado uses RL oxygen from esteban+05, +09
    }

    \begin{longtable}{lllll}
    \hline
    galaxy & region & C/O & O/H & study \\
    \hline
    NGC 6822 & region V & $-0.15 \pm 0.21$ & $-0.44 \pm 0.09$ & peimbert+05 \\
    MW & Sh 2-311 & $-0.10 \pm 0.13$ & $-0.24 \pm 0.04$ & mendez-delgado+22 \\
    MW & NGC 2579 & $-0.15 \pm 0.09$ & $-0.25 \pm 0.03$ & mendez-delgado+22 \\
    MW & NGC 3576 & $-0.03 \pm 0.10$ & $-0.07 \pm 0.06$ & mendez-delgado+22 \\
    MW & NGC 3603 & $0.03 \pm 0.12$ & $-0.09 \pm 0.05$ & mendez-delgado+22 \\
    MW & M8 & $0.03 \pm 0.10$ & $-0.10 \pm 0.04$ & mendez-delgado+22 \\
    MW & M16 & $0.03 \pm 0.16$ & $-0.01 \pm 0.06$ & mendez-delgado+22 \\
    MW & M17 & $0.25 \pm 0.08$ & $-0.05 \pm 0.04$ & mendez-delgado+22 \\
    MW & M20 & $0.02 \pm 0.26$ & $-0.10 \pm 0.07$ & mendez-delgado+22 \\
    MW & M42 & $0.03 \pm 0.08$ & $-0.16 \pm 0.03$ & mendez-delgado+22 \\
    M101 & H1013 & $0.17 \pm 0.07$ & $-0.24 \pm 0.02$ & skillman+20 \\
    M101 & H1052 & $0.13 \pm 0.04$ & $-0.24 \pm 0.01$ & skillman+20 \\
    M101 & NGC 5461 & $-0.10 \pm 0.12$ & $-0.33 \pm 0.02$ & skillman+20 \\
    M101 & NGC 5462 & $-0.18 \pm 0.19$ & $-0.36 \pm 0.05$ & skillman+20 \\
    M101 & NGC 5462 & $-0.07 \pm 0.12$ & $-0.38 \pm 0.01$ & skillman+20 \\
    M101 & NGC 5455 & $-0.13 \pm 0.11$ & $-0.42 \pm 0.02$ & skillman+20 \\
    M101 & NGC 5447 & $-0.09 \pm 0.09$ & $-0.39 \pm 0.01$ & skillman+20 \\
    M101 & NGC 5447 & $-0.04 \pm 0.17$ & $-0.46 \pm 0.01$ & skillman+20 \\
    M101 & H1216 & $-0.42 \pm 0.50$ & $-0.55 \pm 0.03$ & skillman+20 \\
    M101 & NGC 5471 & $-0.26 \pm 0.46$ & $-0.67 \pm 0.03$ & skillman+20 \\
    NGC 300 & R20 & $-0.01 \pm 0.22$ & $-0.12 \pm 0.11$ & toribo-san-cipriano+16 \\
    NGC 300 & R23 & $-0.22 \pm 0.23$ & $-0.11 \pm 0.13$ & toribo-san-cipriano+16 \\
    NGC 300 & R14 & $-0.15 \pm 0.21$ & $-0.19 \pm 0.11$ & toribo-san-cipriano+16 \\
    NGC 300 & R2 & $-0.31 \pm 0.22$ & $-0.24 \pm 0.12$ & toribo-san-cipriano+16 \\
    M33 & NGC 588 & $-0.26 \pm 0.19$ & $-0.32 \pm 0.09$ & toribo-san-cipriano+16 \\
    M33 & IC 132 & $-0.12 \pm 0.15$ & $-0.34 \pm 0.12$ & toribo-san-cipriano+16 \\
    LMC & 30 Dor & $-0.29 \pm 0.06$ & $-0.28 \pm 0.04$ & toribo-san-cipriano+17 \\
    LMC & N44C & $-0.22 \pm 0.03$ & $-0.23 \pm 0.02$ & toribo-san-cipriano+17 \\
    LMC & IC 2111 & $-0.21 \pm 0.08$ & $-0.20 \pm 0.07$ & toribo-san-cipriano+17 \\
    LMC & NGC 1714 & $-0.24 \pm 0.07$ & $-0.25 \pm 0.07$ & toribo-san-cipriano+17 \\
    LMC & N11B & $-0.27 \pm 0.04$ & $-0.22 \pm 0.02$ & toribo-san-cipriano+17 \\
    SMC & N66A & $-0.46 \pm 0.06$ & $-0.46 \pm 0.03$ & toribo-san-cipriano+17 \\
    SMC & N81 & $-0.46 \pm 0.04$ & $-0.47 \pm 0.02$ & toribo-san-cipriano+17 \\
    SMC & NGC 456 & $-0.41 \pm 0.19$ & $-0.45 \pm 0.09$ & toribo-san-cipriano+17 \\
    SMC & N88A & $-0.33 \pm 0.03$ & $-0.59 \pm 0.02$ & toribo-san-cipriano+17 \\
    NGC 6822 & centre & $-0.31 \pm 0.15$ & $-0.46 \pm 0.05$ & esteban+14 \\
    NGC 5408 & centre & $-0.41 \pm 0.19$ & $-0.60 \pm 0.04$ & esteban+14 \\
    M31 & K932 & $0.05 \pm 0.16$ & $-0.19 \pm 0.03$ & esteban+09 \\
    M33 & NGC 595 & $0.05 \pm 0.17$ & $-0.12 \pm 0.05$ & esteban+09 \\
    M33 & NGC 604 & $0.01 \pm 0.14$ & $-0.21 \pm 0.03$ & esteban+09 \\
    NGC 2366 & NGC-2363 & $-0.08 \pm 0.14$ & $-0.77 \pm 0.05$ & esteban+09 \\
    NGC 2403 & VS 24 & $0.30 \pm 0.28$ & $-0.44 \pm 0.04$ & esteban+09 \\
    NGC 2403 & VS 38 & $0.42 \pm 0.20$ & $-0.52 \pm 0.05$ & esteban+09 \\
    NGC 2403 & VS 44 & $-0.08 \pm 0.22$ & $-0.20 \pm 0.04$ & esteban+09 \\

    \hline
    \end{longtable}

\end{table}
